%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{accsupp}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[x11names]{xcolor}
\usepackage{fontawesome5}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\labelitemi}{\color{Green2}\boldmath$>$}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{SeaGreen4}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeBullet}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{c@{\extracolsep{\fill}} r }
      \small\textbf{#1} \headingcap{#3} \ \ \ #2 &  \raggedleft\textit{\small #4} 
    \end{tabular*}
    \small#5
}
\newcommand{\resumeSubheadingOld}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} \headingcap{#3 \vspace{-2pt}} & #2  \\
      \small#5 & \textit{\small #4} 
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadingThin}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small\textbf{#1:} #3 & \small\textit{#2} 
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadingSummary}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \textit{\small #4}
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\summarysepalt}{ --$\bullet$-- }
\newcommand{\summarysep}{ \textcolor{black!50}{$ \backslash \backslash $ }}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\urlstyle{cyan}
\hypersetup{urlcolor=cyan}
\newcommand{\mysite}{www.github.com/natetheadequate}
\newcommand{\myemail}{natewhite345@gmail.com}
\newcommand{\link}[2]{\color{cyan}{\underline{\href{#1}{#2}}}}
\newcommand{\headingcap}[1]{\space \space \space \textit{#1}}
\newcommand{\ghlink}[1]{\href{https://www.github.com/natetheadequate/#1}{
\faIcon{github}/#1}}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{p{5cm} @{\extracolsep{\fill}} p{5cm} @{\extracolsep{\fill}} r}
  \href{https://www.github.com/natetheadequate}{\faIcon{github} natetheadequate} & \textbf{\Large Nathaniel White} & \href{mailto:\myemail}{\myemail{}} \\
  \hline
  \multicolumn{3}{c}{\rule{0pt}{1.5em}\color{Yellow4}\large\textit{Seeking a co-op for January 2023 -- June 2023}}
\end{tabular*}\vspace*{-22pt}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
     \resumeSubheadingSummary{Northeastern University, Khoury College of Computer Sciences, Honors}{Boston, MA}{\BeginAccSupp{ActualText=Candidate for a Bachelor of Science in Computer Science and Mathematics}Candidate for a B.\,S. in Computer Science \& Mathematics\EndAccSupp{}\summarysep{} Physics Minor \summarysep{} 3.87 GPA}{Aug. 2021 -- Dec. 2025}
    \resumeSubheadingSummary
      {Holliston High School}{Holliston, MA}
      { Track/XC \summarysep NHS \summarysep Science Olympiad \summarysep SAT: 1570 \summarysep National Merit Finalist}{Aug. 2017 -- May 2021}
   \resumeSubHeadingListEnd

\section{Computer Knowledge}
  \resumeSubHeadingListStart
  \resumeSubItem{Web Dev}{React, MaterialUI, JavaScript, HTML/CSS, PHP, MySQL, 
  REST API, Express, Jest, Node }
  \resumeSubItem{Scientific Computing}{Lean (Formal Verification), Slurm/HPC, TensorFlow, \LaTeX, Schrodinger Maestro }
  \resumeSubItem{General}{Java, Racket, Python, Linux, Bash, Git, C, Cuda, VEX RobotC, Git, Github, QtPy}
  \resumeSubHeadingListEnd

  \section{Coursework\small\headingcap{* := in progress}}
  \resumeSubHeadingListStart
    \resumeSubItem{CS}
      {Object Oriented Design, Algorithms, Networks and Distributed Systems*, Logic and Computation*}
    \resumeSubItem{Math}
      {Calculus 3, Linear Algebra, Probability \& Statistics, Statistics \& Stochastic Processes*, Group Theory*}
    \resumeSubItem{Physics}{Physics 1, (Mechanics, Basic fluid dynamics), Physics 2 (Waves, Electricity, Magnetism)}
  \resumeSubHeadingListEnd

  \section{Projects\small\headingcap{* := in progress}}
  \resumeSubHeadingListStart
  \resumeSubheading{ML Excitation Model*}{Email for code}{Python, Maestro, MATLAB, Bash, TensorFlow}{Aug. 2022 -- Present}{Identify what aspects of chloramide, flavins, and styrene influence their excitation wavelengths when they are in proximity to each other. Have written a matlab/python script that transforms the raw coordinates of each atom into more usable and interpretable features, which then can be used as input for a neural network or rounded for use in a neural network to predict excitation wavelengths and strengths. }
  \resumeSubheading{Automated Docker}{\ghlink{automated\_docking\_script}}{Python, Maestro, Slurm, QtPy}{July 2022}{Designed a GUI add-on and backend script for Schrodinger Maestro that automated a time-consuming and error-prone process of generating docking poses for three molecules in all permutations.}
  \resumeSubheading{N-Bullets in Racket}{\ghlink{nbulletsrkt}}{Racket}{Apr. 2022}
  {Rewrote a project for a Java-based course in Racket to compare the two languages. Racket was terser, easier to properly test, and (subjectively) more readable. Additional findings and opinions are in the README.}
  \resumeSubheading{Grave Finder}{\ghlink{findagravemiddleborough.ml}}{ReactJS, PHP, MySQL, Cloudflare, cPanel, SSL}{Dec. 2020}{Website to view grave data for a local cemetery preservation nonprofit. Makes use of join tables, searching, filtering, React+MaterialUI forms, an administrator login with a cooldown period after too many login attempts. }
  \resumeSubHeadingListEnd

  \section{Research and Work}
  \resumeSubHeadingListStart
  \resumeSubheadingThin{Peer Tutoring}{Sep. 2022 -- Present}{Discrete, Fundies 1 \& 2, OOD, Algo, Phys 2, Calc 3, LinAlg, Prob \& Stats}
  \resumeItemListStart
    \resumeBullet{Demonstrate patience and professionalism with tutees having a variety of skill levels}
    \resumeBullet{Generate new ways to explain content}
  \resumeItemListEnd
  \resumeSubheadingThin{Sijia Dong Lab}{Dec. 2021 -- Present}{Computational chemistry research group}
  \resumeItemListStart
    \resumeBullet{Bypass time-consuming processes and calculations using automation scripts and ML}
    \resumeBullet{Listen and understand technical constraints and communicate progress and possible avenues for progress}
  \resumeItemListEnd
  \resumeSubheadingThin{Internship with Town of Holliston Director of Technology}{Nov. 2020 -- Feb. 2021, Apr. 2021 -- May 2021}{}
  \resumeItemListStart
    \resumeBullet{Implement proper settings and software on new desktops for various town departments such as the police and the senior center}
    \resumeBullet{Resolve problems with phones, printers, and file storage for various town employees}
  \resumeItemListEnd
  \resumeSubheadingThin{Kitchen Worker at Hannah BG Shaw Home for the Aged}{June 2020 -- Aug 2021}{Server, dishwasher \& cook} \resumeItemListStart
  \resumeBullet{Fulfill resident requests in compliance with dietary restrictions}
  \resumeBullet{Exhibit patience and communicate clearly in a fast-paced environment}
  \resumeItemListEnd \resumeSubHeadingListEnd

  \section{Interests and Other Skills} 
  \resumeSubHeadingListStart
    \item\small{B2 Proficiency in French \summarysep
    Proofs\./\.logic \summarysep Climate emergency \summarysep Running \summarysep Amateur cooking  \summarysep Political economy }
    \resumeSubHeadingListEnd
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}